---
title: "Getting Started with rdataviz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with rdataviz}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

## Introduction

rdataviz provides publication-quality themes and colorblind-safe palettes for R data visualization. This vignette covers the basics of using the package.
## Installation

```{r eval=FALSE}
# Install from GitHub
remotes::install_github("user/rdataviz")
```

## Basic Usage

```{r setup}
library(rdataviz)
library(ggplot2)
```

### Applying the Theme

The main theme function is `theme_worldclass()`:

```{r theme-example}
ggplot(mtcars, aes(wt, mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  labs(
    title = "Weight vs Fuel Efficiency",
    subtitle = "Data from Motor Trend magazine, 1974",
    x = "Weight (1000 lbs)",
    y = "Miles per Gallon",
    color = "Cylinders"
  ) +
  scale_color_rdataviz() +
  theme_worldclass(dark_mode = FALSE)
```

### Dark Mode

For presentations or dashboards with dark backgrounds, use `dark_mode = TRUE`.
Note: Dark mode is optimized for display on dark backgrounds (Shiny apps, slides).

```{r dark-mode, eval=FALSE}
# Same plot with dark mode (not rendered in vignette)
ggplot(mtcars, aes(wt, mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  scale_color_rdataviz() +
  theme_worldclass(dark_mode = TRUE)
```

## Color Palettes

### Categorical Data

Use `scale_fill_rdataviz()` or `scale_color_rdataviz()`:

```{r categorical}
ggplot(iris, aes(Species, Sepal.Length, fill = Species)) +
  geom_boxplot() +
  scale_fill_rdataviz() +
  theme_worldclass(dark_mode = FALSE) +
  labs(title = "Sepal Length by Species")
```

### Health/Risk Data

Use the diabetes palette for health status:

```{r health}
health_data <- data.frame(
  status = c("No Diabetes", "Prediabetes", "Diabetes"),
  count = c(850, 100, 50)
)

ggplot(health_data, aes(status, count, fill = status)) +
  geom_col() +
  scale_fill_rdataviz("diabetes") +
  theme_worldclass(dark_mode = FALSE) +
  labs(title = "Health Status Distribution")
```

### Continuous Risk Gradient

For heatmaps or continuous risk scores:

```{r risk}
risk_data <- expand.grid(x = 1:10, y = 1:10)
risk_data$value <- (risk_data$x + risk_data$y) / 20

ggplot(risk_data, aes(x, y, fill = value)) +
  geom_tile() +
  scale_fill_risk() +
  theme_worldclass(dark_mode = FALSE) +
  labs(title = "Risk Heatmap")
```

## Available Palettes

| Palette | Colors | Use Case |
|---------|--------|----------|
| `chart_colors` | 10 | General categorical data |
| `diabetes_colors` | 3 | Health status (healthy/warning/risk) |
| `risk_gradient` | 6 | Sequential risk levels |
| `subgroup_colors` | 5 | Population subgroups |

## Theme Customization

Adjust base size for different contexts:

```{r customization}
# Larger text for presentations
ggplot(mtcars, aes(wt, mpg)) +
  geom_point() +
  theme_worldclass(base_size = 18, dark_mode = FALSE)
```

## Learn More

- See `?theme_worldclass` for all theme options
- See `?scale_fill_rdataviz` for scale functions
- See `?get_theme_colors` for programmatic color access
